---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/err.svg?branch=master)](https://travis-ci.com/poissonconsulting/err)
[![Coverage status](https://codecov.io/gh/poissonconsulting/err/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/err?branch=master)

## Introduction

`err` is an R package to produce number sensitive error and warning messages.

## Utilisation

```{r, error=TRUE}
library(err)

x <- 1:6
err(cn_and(x, "the %n erroneous values are: %c"))
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/err)
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/err")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("err")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "err")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/err/issues).

[Pull requests](https://github.com/poissonconsulting/err/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.

## Inspiration

[`concatenate`](https://github.com/jamesdunham/concatenate) by [James Dunham](https://github.com/jamesdunham)


